Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2022-06-25 doc/JFLA2022/Slides/Slides.tex
last changes in Slides ?

\begin{scope}[yshift=-5cm,xshift=4cm]
  \node[rectangle, draw=black,fill=red!60,minimum height=0.5cm,minimum width=1.5cm] (book) {hydras.pdf};
    \node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm, left of=book, node distance=6cm] (latex) {hydras.tex};
\end{scope}

@@

\begin{frame}
  \frametitle{The Ketonen-Solovay machinery\footnote{Rapidly Growing {R}amsey Functions (1981)}}
    \begin{block}{Formalization}
      {\color{mathcolor}
      $$\omega^{\omega^2+1}+1 \rplus{1} \omega^{\omega^2+1}
      \rplus{2} \omega^{\omega^2}\times 3 
      \rplus{3} \omega^{\omega^2}\times 2 +
      \omega ^ {\omega \times 4}, \dots,2,1,0$$

@@

      \begin{block}{Small steps}
        At the $i$-th round, 
           \textcolor{mathcolor}{$\alpha \rplus{i} \canonseq{\alpha}{i}$},
           where \textcolor{mathcolor}{$\canonseq{\alpha}{\_}$} is the \emph{canonical sequence} of \textcolor{mathcolor}{$\alpha$}.

@@

    Canonical sequences are implemented by a structurally recursive function on terms in Cantor normal form.

@@

       \item     If \textcolor{mathcolor}{$\alpha \rplus{n,n,\dots,n} \beta$} then \textcolor{mathcolor}{$H'_\beta(n)\leq H'_\alpha(n)$}

>>>>

\begin{scope}[yshift=-5cm,xshift=4cm]
  \node[rectangle, draw=black,fill=orange!80,minimum height=0.5cm,minimum width=1.5cm] (book) {hydras.pdf};
    \node[rectangle, draw=black,fill=orange!80,minimum height=0.5cm,minimum width=1.5cm, left of=book, node distance=6cm] (latex) {hydras.tex};
\end{scope}

@@

\begin{frame}
  \frametitle{The Ketonen-Solovay machinery\footnote{Rapidly Growing {R}amsey Functions (1981)}}
    \begin{block}{Paths associated with hydra battles}
      {\color{mathcolor}
      $$\omega^{\omega^2+1}+1 \rplus{1} \omega^{\omega^2+1}
      \rplus{2} \omega^{\omega^2}\times 3 
      \rplus{3} \omega^{\omega^2}\times 2 +
      \omega ^ {\omega \times 4}, \dots,2,1,0$$

@@

      \begin{block}{}
        At the $i$-th round, 
           \textcolor{mathcolor}{$\alpha \rplus{i} \canonseq{\alpha}{i}$},
           where \textcolor{mathcolor}{$\canonseq{\alpha}{\_}$} is the \emph{canonical sequence} of \textcolor{mathcolor}{$\alpha$}.

@@

    Canonical sequences are implemented by a structurally recursive function on ordinal terms in Cantor normal form.

@@

       \item     If \textcolor{mathcolor}{$\alpha \rplus{i,i,\dots,i} \beta$} then \textcolor{mathcolor}{$H'_\beta(i)\leq H'_\alpha(i)$}.
